\documentclass[10pt, twocolumn]{report}

\usepackage{color}
\usepackage[toc,page]{appendix}
\usepackage{authblk}
\usepackage{amsmath}
\usepackage{url}
\usepackage{graphicx}
\usepackage{float}
\usepackage{listings}

\definecolor{mygray}{rgb}{0.4,0.4,0.4}

\lstdefinestyle{cppStyle}{
	captionpos=b,
	numbers=left,
	% xleftmargin=8pt,
	numberstyle=\color{mygray}\ttfamily\tiny,
	numbersep=8pt,
	language=c++,
	keywordstyle=\color{blue}\tiny,
	stringstyle=\color{red}\tiny,
	commentstyle=\color{green}\tiny,
	basicstyle=\ttfamily\tiny,
	showstringspaces=false,
	breaklines,
	escapechar=|,
	columns=fullflexible,
}

\begin{document}

\title{Bubble Sort and Linear Regression with MPI}

\author[1]{Claudio Scheer}
\author[1]{Gabriell Araujo}
\affil[1]{Master's Degree in Computer Science - PUCRS}
\affil[ ]{\textit{\{claudio.scheer, grabriell.araujo\}@edu.pucrs.br}}

\maketitle

\section {General Setup}
Instead of using the LAD access provided by the professor, we ran our \textit{batch job} on two nodes in the Cerrado cluster. That is because we developed in C++17 and needed a newer version of GCC and OpenMPI than the one provided by LAD, and we already had a \textit{batch job} configured from previous works.

\section{Bubble Sort}
The bubble sort problem addressed here consists of sorting 1000 vectors with 2500 integers.

\section {Linear Regression}
Linear regression is an algorithm used for predictive analysis. In summary, the algorithm finds a relationship between $x$ and $y$ and can predict a new $y$ using as input a $x$ not yet known by the model. To test the algorithm, we used 100000000 $x$ and $y$ points.

\section{Results}
Results of your interviews or observations. Use information and/or quotes from your interview or observations.

\begin{appendices}
	\chapter{Bubble Sort Source Code}
	\lstinputlisting[caption=Dataset generator,style=cppStyle]{../bubble-sort/dataset-generator.cpp}
	\lstinputlisting[caption=Bubble Sort Sequential,style=cppStyle]{../bubble-sort/sort-seq.cpp}
	\lstinputlisting[caption=Bubble Sort MPI,style=cppStyle]{../bubble-sort/sort-mpi.cpp}

	\chapter{Linear Regression Source Code}
	\lstinputlisting[caption=Dataset generator,style=cppStyle]{../bubble-sort/dataset-generator.cpp}
	\lstinputlisting[caption=Linear Regression Sequential,style=cppStyle]{../linear-regression/lr-seq.cpp}
	\lstinputlisting[caption=Linear Regression MPI,style=cppStyle]{../linear-regression/lr-mpi.cpp}
\end{appendices}

\end{document}
